---
title: "Chapter N — Topic"
subtitle: "Template slide deck (Python ↔ R)"
format:
  revealjs:
    output-file: template-slides.html
    theme: simple
    slide-number: true
    incremental: false
    smaller: true
    scrollable: true
  html: default
---

# Section heading {.section}

A section divider slide. Replace with the section title for the chapter
this deck covers.

## A regular slide

Regular content slides start at H2.

- Bullet
- Bullet
- Bullet

## Python ↔ R code, side-by-side

::: {.panel-tabset}

### Python

```{python}
#| eval: false
# Replace this with the example for the chapter the deck covers.
import numpy as np
x = np.arange(1, 6)
x.mean()
```

### R

```{r}
#| eval: false
# Replace this with the R equivalent.
x <- 1:5
mean(x)
```

:::

`{.panel-tabset}` is Quarto's standard tab block. Anything inside `:::`
becomes one tab; the H3 headings (`### Python`, `### R`) are the tab
labels. Switch the active tab without re-rendering the slide.

## A second tabset slide

::: {.panel-tabset}

### Python

```{python}
#| eval: false
# Example 2
```

### R

```{r}
#| eval: false
# Example 2
```

:::

## How to add a new chapter deck

1. Copy `template.qmd` to `slides/ChNN-<topic>.qmd`.
2. Update the YAML `title`, `subtitle`, and
   `revealjs.output-file: ChNN-<topic>-slides.html`.
3. Replace the template slides with chapter content (subject to the IP
   discussion in `slides/index.qmd`).
4. Add the deck to the navbar in the project root `_quarto.yml`.
